Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
fixed 6

Our analysis of SMBH feedback has focused on Compton heating
instead of kinetic feedback, since the effects of radiative feedback
are relatively straightforward to calculate from the properties of the
accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion.  Our simple
parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assuming heating which is volumetrically uniform predicts an
effectic wind velocity which increases with SMBH mass as
$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
galaxies, respectively.  Coupled with the dependence of the SMBH
accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto
M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass};
eq.~[\ref{eq:eddr_analytic}]), a dominant source of kinetic feedback of the form we have
adopted leads to an Eddington ratio dependence on SMBH mass of
$\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.

This prediction is also consistent with the observed dependence of $\langle
L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
(Fig.~\ref{fig:miller}, green line), hinting that accretion regulation
by kinetic feedback may serve as an alternative explanation for X-ray
luminosities of elliptical galaxies.  However, our assumption that
kinetic outflows heat the gas uniformly in volume is somewhat
arbitrary and would need to more rigorously justified by numerical
studies of how jets or disk outflows couple energy to their gaseous
environment.  It is furthermore unclear whether our steady-state model
can be applied at all, because black hole feedback depends on the
central accretion rate, which (unlike stellar feedback) does not
respond instantaneously to changes in the thermodynamic properties of
the gas on larger scales.

>>>>

Our analysis of SMBH feedback has focused on Compton heating
instead of kinetic feedback, since the effects of radiative feedback
are relatively straightforward to calculate from the properties of the
accretion flow.  However, it is possible kinetic feedback from SMBH outflows could play an equal or greater role in regulating accretion, even in low luminosity AGN.

Our simple parameterization of kinetic feedback (eq.~[\ref{eq:vjet}]) assumes a uniform volumetric heating and predicts an
effective wind velocity which increases with SMBH mass as
$v_{w}^{\bullet} \propto M_{\bullet}^{0.33(0.28)}$ for core(cusp)
galaxies, respectively.  Coupled with the dependence of the SMBH
accretion rate on the wind heating, $\dot{M}/\dot{M}_{\rm edd} \propto
M_{\bullet}^{0.76(0.48)}v_{w}^{-3.8(-2.4)}$ (Fig.~\ref{fig:mdot_mass};
eq.~[\ref{eq:eddr_analytic}]), a dominant source of kinetic feedback of the form we have
adopted leads to an Eddington ratio dependence on SMBH mass of
$\dot{M}/\dot{M}_{\rm edd} \propto M_{\bullet}^{-0.5(-0.2)}$.

This prediction is also consistent with the observed dependence of $\langle
L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
(Fig.~\ref{fig:miller}, green line), suggesting that accretion regulation
by kinetic feedback could play a role in determining the X-ray
luminosities of elliptical galaxies.  However, our assumption that
kinetic outflows heat the gas uniformly in volume is rather arbitrary and would need to more rigorously justified by numerical studies of how jets or disk outflows couple energy to their gaseous
environment.  As already discussed, it is furthermore unclear whether a steady-state accretion model is at all relevant in the case when SMBH feedback dominates due to the time delay between the small scale accretion flow and the thermodynamic response of the CNM on larger scales.
